Enhancement of SDR in Thessaloniki

### 2024-03-12 GHI_enh_04_investigate.tex
Commit 2024-03-12 17:11

\begin{verbatim}
Warning: The dot-dot notation (`..count..`) was deprecated in ggplot2 3.4.0.
i Please use `after_stat(count)` instead.
This warning is displayed once every 8 hours.
Call `lifecycle::last_lifecycle_warnings()` to see where this warning was generated.
\end{verbatim}

@@

@@

@@

\begin{verbatim}
2024-03-12 10:27:22.9 athan@tyler GHI_enh_04_investigate.R 1.200812 mins
\end{verbatim}

>>>>

@@

\begin{verbatim}
Warning in scale_y_log10(): log-10 transformation introduced infinite values.
\end{verbatim}

\begin{verbatim}
Warning: Removed 25 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Scale for x is already present.
Adding another scale for x, which will replace the existing scale.
\end{verbatim}

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}

\begin{verbatim}
Scale for x is already present.
Adding another scale for x, which will replace the existing scale.
\end{verbatim}

\begin{verbatim}
Warning: Removed 5 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-10} \end{center}

@@

\begin{verbatim}
2024-03-12 15:10:56.3 athan@tyler GHI_enh_04_investigate.R 2.333127 mins
\end{verbatim}
